---
title: "Initial Korean covid 19"
author: "Kathleen Castro"
date: "03/30/2023"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
kRdata <- kRdata %>%
mutate(across(where(is.character), as.factor))

```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 2020
### This data was retrieved from a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Your Question - Is dying independent of sex?






## Graphical results - use ggplot commands to do this  


```{r}
barchartGC(~result + Sex,data=kRdata)
barchartGC(~result + Sex,data=kRdata, type="percent")

```
    
Looking at the bar graph above, we can see that there are more males dying over the amount of females. The percentage for the males alive have a lower percentage compared to women. Taking a look at the frequency where the total amount of people are given, we can see that women have a higher rate of being alive when being compared to the men from this data.
  
  
## Numerical results

```{r}
table1 <- xtabs(~result + Sex, data=kRdata)
rowPerc(table1)
colPerc(table1)
```
  
Now taking a look at the data presented above, we see the total of 36% of females dead leaving 64% of males dying. When looking at the percentages on being alive, females are at 56% while males are left at 44%.

## Inferential results 

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
  

## Conclusions

